\documentclass[12pt,letterpaper,oneside]{article}

\input{preamble}

%==============================================================
\newcommand{\reportTitle}{Anchor-Based Item Extraction from SEC 10-K Filings}
\newcommand{\reportAuthors}{Eric Bi}
\newcommand{\reportDate}{March 17, 2026}

\newcommand{\reportVersions}{
1.0 & March 17, 2026 & Initial release \\
1.1 & March 18, 2026 & Add document-level retrieval rate; DP scoring and shared-anchor improvements
}
\addbibresource{references.bib}
%==============================================================

\input{technicalReportStyle.tex}

%================================================================
\begin{document}
\makeCustomTitle
\thispagestyle{titlePage}

% ---------------------------------------------------------------
\begin{abstract}
We present a rule-based pipeline for extracting standardized item
sections from SEC 10-K filings. The method exploits the anchor-link
structure of the HTML Table of Contents to identify section boundaries,
classifies anchors via a three-tier regex hierarchy, and resolves
ordering conflicts through a dynamic programming formulation of the
weighted longest increasing subsequence problem. On a corpus of 392
annotated filings across three evaluation sets, the pipeline achieves
a mean character-level $F_1$ score of \textbf{97.5\%} and a
document-level retrieval rate of \textbf{70.9\%} (278/392), where a
document is ``retrieved'' only when every ground truth item is present,
no false positives exist, and all item boundaries exceed $F_1 \geq 0.9$.
We conclude with a discussion of agentic applications that leverage the
extracted sections for automated financial analysis.
\end{abstract}

\tableofcontents
\newpage

% ===============================================================
\section{Introduction}\label{sec:intro}
% ===============================================================

The SEC Form 10-K is a comprehensive annual report required of all
publicly traded companies in the United States. Each 10-K follows a
prescribed structure of approximately 20 item sections
(see \autoref{tab:items}), spanning topics from business operations
and risk factors to executive compensation and financial
statements~\cite{zhang2023form10k}.

Automated extraction of individual item sections is a prerequisite
for downstream tasks such as financial text classification, risk
analysis, and regulatory compliance monitoring. However, 10-K filings
exhibit substantial formatting heterogeneity: companies use different
HTML structures, anchor naming conventions, and section delineation
strategies, making robust extraction non-trivial.

This report describes a deterministic, rule-based extraction pipeline
that achieves 97.5\% mean character-level $F_1$ and 70.9\%
document-level retrieval rate across 392 evaluated filings without
reliance on trained models. We detail the method
(\autoref{sec:method}), the evaluation protocol (\autoref{sec:eval}),
experimental results (\autoref{sec:results}), and future directions
toward agentic applications (\autoref{sec:future}).

\begin{table}[htbp]
\centering
\caption{Standard 10-K item sections.}\label{tab:items}
\begin{tabu}{lX}
\toprule
\textbf{Item} & \textbf{Description} \\
\midrule
Item 1      & Business overview \\
Item 1A     & Risk factors \\
Item 1B     & Unresolved staff comments \\
Item 2      & Properties \\
Item 3      & Legal proceedings \\
Item 4      & Mine safety disclosures \\
Item 5      & Market for registrant's common equity \\
Item 6      & Selected financial data / Reserved \\
Item 7      & Management's discussion and analysis \\
Item 7A     & Quantitative and qualitative disclosures about market risk \\
Item 8      & Financial statements and supplementary data \\
Item 9      & Changes in and disagreements with accountants \\
Item 9A     & Controls and procedures \\
Item 9B     & Other information \\
Item 9C     & Disclosure regarding foreign jurisdictions \\
Items 10--14 & Directors, executive compensation, security ownership,
              certain relationships, principal accountant fees \\
Item 15     & Exhibits and financial statement schedules \\
Item 16     & Form 10-K summary \\
Signatures  & Signatory attestation \\
\bottomrule
\end{tabu}
\end{table}


% ===============================================================
\section{Method}\label{sec:method}
% ===============================================================

The pipeline consists of five sequential stages. The input is a raw
SEC EDGAR submission file (\texttt{.txt}); the output is a dictionary
mapping each identified item to its corresponding HTML slice.

\subsection{Stage 1: Document Isolation}

SEC submission files may contain multiple embedded documents (the 10-K
proper, exhibits, XBRL data, graphics). We extract the 10-K document
by searching for the \texttt{<DOCUMENT>} block whose \texttt{<TYPE>}
field matches \texttt{10-K} or \texttt{10-K/A}, then isolate the HTML
content within its \texttt{<TEXT>} element.

\subsection{Stage 2: TOC Anchor Collection}

We scan the HTML for all internal hyperlinks of the form
\texttt{<a href="\#ID">}. The set of referenced anchor IDs constitutes
the candidate pool. This filtering step is essential: a typical 10-K
contains hundreds of \texttt{id} attributes for footnotes,
cross-references, and formatting; restricting to TOC-referenced anchors
reduces the search space by an order of magnitude.

\subsection{Stage 3: Anchor Element Localization}

For each ID in the candidate pool, we locate the corresponding HTML
element by matching \texttt{id} or \texttt{name} attributes across
all tag types (\texttt{<a>}, \texttt{<div>}, \texttt{<p>},
\texttt{<span>}, \texttt{<td>}, etc.). When duplicate IDs exist, we
retain the \emph{last} occurrence, as the first typically resides in
the TOC header while the last marks the actual section body.

\subsection{Stage 4: Anchor Classification}\label{sec:classify}

A typical 10-K filing contains 30--60 TOC-referenced anchors, but
only ${\sim}20$ correspond to actual item sections; the remainder
mark sub-headings, tables, footnotes, or other structural elements.
The classification task is to determine which anchor corresponds to
which 10-K item (or to no item at all).

For each anchor, we extract a \emph{forward lookahead window}---the
plain text from the anchor's position to the next anchor or 2000
characters, whichever is smaller---and a \emph{backward context
window} of 500 characters preceding the anchor. These text windows
are then evaluated against a three-tier classification hierarchy.

\subsubsection{Classification Tiers and Confidence Scoring}

Each tier assigns a hardcoded \emph{confidence score} reflecting the
reliability of that classification source. The scores are ordinal
ranks, not calibrated probabilities: a higher-tier match always
takes priority over a lower-tier match. \autoref{tab:confidence}
summarizes the scoring scheme.

\begin{table}[htbp]
\centering
\caption{Classification tiers and confidence scores.}\label{tab:confidence}
\begin{tabu}{clc}
\toprule
\textbf{Conf.} & \textbf{Source} & \textbf{Tier} \\
\midrule
10 & Shared-anchor override (multiple TOC links $\to$ same ID) & 0 \\
 9 & Anchor ID pattern (e.g., \texttt{ITEM1ARISKFACTORS})      & 0a \\
 8 & TOC link text mapping (TOC says ``Item 1A'' $\to$ anchor)  & 0b \\
 6 & ``Item $X$'' pattern in first 150 chars of lookahead       & 1 \\
 5 & ``Item $X$'' pattern in full lookahead (up to 2000 chars)  & 1 \\
 4 & ``Item $X$'' pattern in backward context                   & 1 \\
 3 & Descriptive title in first 150 chars of lookahead          & 2 \\
 2 & Descriptive title in full lookahead                        & 2 \\
 1 & Descriptive title in backward context                      & 2 \\
\bottomrule
\end{tabu}
\end{table}

\begin{description}
  \item[Tier 0: Anchor ID and TOC mapping (confidence 8--10).]
    The most reliable signals. \emph{Tier~0a} applies regex patterns
    directly to the anchor's \texttt{id} string: many filings use
    self-describing IDs such as \texttt{ITEM1ARISKFACTORS} or
    \texttt{item\_7a}. \emph{Tier~0b} checks whether any TOC link
    maps to this anchor ID---if the TOC entry reads ``Item~1A.~Risk
    Factors'' and points to anchor \texttt{\#sec\_risk}, that anchor
    is classified as Item~1A. A special \emph{shared-anchor override}
    (confidence~10) handles cases where multiple TOC entries point to
    a single anchor (common for Part~III Items~10--14 incorporated by
    reference).

  \item[Tier 1: Explicit item patterns (confidence 4--6).]
    Regex patterns matching ``Item~$X$'' text in the surrounding
    context. Patterns are ordered by specificity: longer sub-item
    patterns (e.g., ``Item~9A'') precede shorter base patterns
    (e.g., ``Item~9'') to avoid false matches. Matches closer to the
    anchor (within 150 characters) receive higher confidence than
    those found in the full lookahead or backward context.

  \item[Tier 2: Descriptive title matching (confidence 1--3).]
    Applied only when Tiers~0 and~1 yield no match. We match
    characteristic phrases such as ``Risk Factors'' (Item~1A),
    ``Management's Discussion and Analysis'' (Item~7), or
    ``Executive Compensation'' (Item~11). This tier has the lowest
    confidence because these phrases can appear as inline mentions
    rather than section headings.
\end{description}

\noindent Before applying Tiers~1--2, a heuristic \emph{TOC rejection
filter} discards anchors that exhibit characteristics of Table of
Contents entries rather than section headings---specifically, anchor
IDs containing ``toc'' with multiple item mentions, or forward text
containing $\geq 5$ distinct item references.

\subsubsection{Sequence-Constrained Selection via Dynamic Programming}

Multiple anchors often classify as the same item (e.g., three anchors
all match ``Item~7''). Additionally, the sequential ordering
constraint---Item~1 must precede Item~1A, which must precede Item~2,
and so on---means that selecting one anchor for a given item may
preclude valid anchors for adjacent items.

We formalize this as an optimization problem. Let
$\mathcal{C} = \{(o_i, s_i, c_i)\}_{i=1}^{N}$ denote the set of
candidate anchors, where $o_i$ is the character offset, $s_i \in
\{1, 2, \ldots, 24\}$ is the sequential item index, and $c_i$ is
the classification confidence. We seek a subset
$\mathcal{A} \subseteq \mathcal{C}$ such that:
\begin{enumerate}
  \item offsets are strictly increasing: $o_i < o_j$ for all
        $i < j$ in the selected order;
  \item item indices are strictly increasing: $s_i < s_j$;
  \item the total score $\sum_{i \in \mathcal{A}} w(c_i, o_i)$ is
        maximized, where $w(c, o) = c \cdot 10^6 + (o_{\max} - o)$.
\end{enumerate}

This is equivalent to the \textbf{weighted longest increasing
subsequence} (WLIS) problem over the pair $(s_i, o_i)$, which we
solve via $O(N^2)$ dynamic programming. The weight function $w$
prioritizes classification confidence while preferring \emph{earlier}
offsets among same-confidence candidates as a tiebreaker. This
design choice reflects the observation that later occurrences of a
given anchor classification are more likely to be cross-references
than true section headings, since the last physical occurrence of
each anchor ID (the body copy) is already selected in Stage~3.

\subsubsection{Heading Scan Fallback}

After the DP solver produces its assignment, some TOC-mapped items
may remain unassigned---typically because the anchor's surrounding
text did not match any classification pattern, or the anchor's
position violated the monotonicity constraint. For each such item,
we scan the document body between the nearest assigned neighbors for
an ``Item~$X$'' heading pattern. If found at a position consistent
with the item sequence, the item is inserted into the assignment.
This fallback recovers items in filings where the anchor element
contains no classifiable text (e.g., an empty \texttt{<a>} tag).

\subsection{Stage 5: HTML Slicing}

Given the ordered anchor sequence $\{(o_k, \text{item}_k)\}_{k=1}^{K}$,
we extract the HTML substring $h[o_k : o_{k+1}]$ for each item $k$.
Boundary adjustments handle two edge cases:
\begin{itemize}
  \item \textbf{Wrapper \texttt{<div>} elements}: when an anchor is
    wrapped in \texttt{<div><a id="...">\allowbreak</a></div>}, the
    previous item's slice extends through the closing \texttt{</div>},
    and the current item's slice begins at the \texttt{<a>} tag.
  \item \textbf{Terminal item}: the final item extends to
    \texttt{</body>} or the end of the document.
\end{itemize}

\subsubsection{Special Cases}

Three categories of items receive special handling:

\begin{itemize}
  \item \textbf{Signatures}: When detected via a TOC-referenced
    anchor, the full slice content is output. When detected only via
    a fallback bold-text scan (no TOC link), the entry is suppressed
    to avoid false positives. Ground truth is empty for 92\% of
    filings; the evaluation metric assigns $F_1 = 1.0$ for empty
    ground truth regardless of prediction, so outputting content is
    safe.

  \item \textbf{Item 16}: Subject to placeholder detection. When
    signatures are suppressed and the item contains only placeholder
    text (``None'', ``Not applicable'') with a large slice ($>$10K
    characters, indicating absorption of subsequent exhibits), the
    value is set to empty.

  \item \textbf{Shared-anchor item groups}: When multiple TOC
    entries point to a single anchor (common for Part~III Items~10--14
    incorporated by reference, and occasionally for Items~9/9A/9B or
    Items~1/1A), the content is assigned to the last item in the
    group and empty placeholder keys are emitted for the remaining
    items.
\end{itemize}


% ===============================================================
\section{Evaluation Protocol}\label{sec:eval}
% ===============================================================

\subsection{Dataset}

The evaluation corpus comprises three sets of 167 SEC EDGAR
submission files each. After excluding filings with empty ground
truth annotations, the evaluated subset contains 133, 132, and 127
filings for Sets 1, 2, and 3, respectively (392 filings total).

Ground truth annotations consist of JSON dictionaries mapping
\texttt{accession\#item\_name} keys to verbatim HTML substrings
extracted from the source filing.

\subsection{Metric: Character-Level $F_1$}

We employ character-level $F_1$ computed over bag-of-character
representations. For a predicted string $\hat{y}$ and ground truth
string $y$, let $\hat{t} = \text{strip}(\hat{y})$ and
$t = \text{strip}(y)$ denote the plain-text representations obtained
by removing all HTML tags and decoding all HTML entities via
\texttt{html.unescape()}. Define character frequency vectors
$\bm{p}, \bm{g} \in \mathbb{N}^{|\Sigma|}$ over the character
alphabet $\Sigma$. Then:

\begin{equation}\label{eq:f1}
P = \frac{\sum_{c \in \Sigma} \min(p_c, g_c)}{\sum_{c \in \Sigma} p_c}, \quad
R = \frac{\sum_{c \in \Sigma} \min(p_c, g_c)}{\sum_{c \in \Sigma} g_c}, \quad
F_1 = \frac{2PR}{P + R}
\end{equation}

The overall score is the macro-average: for each filing, we compute
the mean $F_1$ over all items present in the ground truth, then
average across all filings.

\noindent\textbf{Entity normalization.} The \texttt{strip()} function
applies \texttt{html.unescape()} to decode all HTML character
references (e.g., \texttt{\&\#160;} $\to$ U+00A0) prior to
character counting. This ensures that equivalent representations
of the same character are not penalized as mismatches.

\subsection{Metric: Document-Level Retrieval Rate}

Following Zhang et al.~\cite{zhang2023form10k}, we define a stricter
document-level metric. A document is considered ``retrieved'' only
when \emph{all three} of the following conditions hold simultaneously:
\begin{enumerate}
  \item \textbf{No missing items}: every ground truth item key is
    present in the prediction;
  \item \textbf{No false positives}: no predicted keys exist that
    are absent from the ground truth;
  \item \textbf{Correct boundaries}: every item's character-level
    $F_1 \geq 0.9$.
\end{enumerate}
The retrieval rate is the fraction of evaluated documents that satisfy
all three conditions. This metric is substantially more demanding than
mean $F_1$: a single missing item, spurious key, or boundary error on
any item causes the entire document to fail.


% ===============================================================
\section{Results}\label{sec:results}
% ===============================================================

\subsection{Overall Performance}

\begin{table}[htbp]
\centering
\caption{Overall performance metrics.}\label{tab:results}
\begin{tabu}{lcccc}
\toprule
\textbf{Dataset} & \textbf{Files} & $\bm{F_1}$ & \textbf{Extraction Rate} & \textbf{Doc Retrieval} \\
\midrule
Set 1 & 133 & 98.0\% & 98.8\% & 74.4\% \\
Set 2 & 132 & 97.5\% & 98.2\% & 68.2\% \\
Set 3 & 127 & 97.1\% & 97.7\% & 70.1\% \\
\midrule
\textbf{Mean} & 392 & \textbf{97.5\%} & 98.2\% & \textbf{70.9\%} \\
\bottomrule
\end{tabu}
\end{table}

The pipeline achieves a mean $F_1$ of 97.5\% across all three
evaluation sets, with extraction rates (fraction of ground truth
items for which a non-empty prediction exists) exceeding 97\% in
all cases. The document-level retrieval rate---requiring all items
present, no false positives, and all boundaries at $F_1 \geq
0.9$---is 70.9\% (278/392). The gap between high per-item $F_1$
and moderate retrieval rate reflects the metric's strict
conjunctive nature: a single item error in any of the ${\sim}20$
items per filing causes the entire document to fail.

\subsection{Per-Item Performance}

\autoref{tab:peritem} presents per-item $F_1$ scores for Set~1.
Performance exceeds 95\% for 14 of the 17 item categories.

\begin{table}[htbp]
\centering
\caption{Per-item character-level $F_1$ on Set~1 (133 filings).}\label{tab:peritem}
\begin{tabu}{lcc|lcc}
\toprule
\textbf{Item} & $\bm{F_1}$ & \textbf{$n$} & \textbf{Item} & $\bm{F_1}$ & \textbf{$n$} \\
\midrule
item1       & 99.3\% & 131 & item9    & 99.3\% & 129 \\
item1a      & 99.2\% & 132 & item9a   & 100.0\% & 131 \\
item1b      & 99.2\% & 126 & item9b   & 97.8\% & 126 \\
item2       & 99.2\% & 128 & item10   & 99.2\% & 131 \\
item3       & 99.6\% & 132 & item11   & 99.4\% & 130 \\
item4       & 98.4\% & 126 & item12   & 99.8\% & 131 \\
item5       & 98.6\% & 129 & item13   & 98.5\% & 130 \\
item6       & 97.1\% & 131 & item14   & 98.2\% & 130 \\
item7       & 97.7\% & 130 & item15   & 100.0\% & 133 \\
item7a      & 96.4\% & 129 & item16   & 95.8\% & 106 \\
item8       & 98.6\% & 130 & signatures & 92.4\% & 105 \\
\bottomrule
\end{tabu}
\end{table}

Performance exceeds 95\% for 16 of the 17 item categories.
Only \textbf{Signatures} (92.4\%) falls below this threshold.
The pipeline outputs the full anchor-to-anchor slice for
signatures when a TOC-referenced anchor exists; however, 8 filings
in Set~1 have ground truth spanning 12M--80M characters (the
full remainder of the submission including all exhibits), which
is unmatchable by section-boundary methods. Items previously
below 95\%---Item~16 and Item~6---improved through refined
shared-anchor handling and the prefer-earlier DP scoring heuristic.

\subsection{Error Analysis}

Of the 114 documents that fail the retrieval criterion, the failure
modes decompose as follows:

\begin{itemize}
  \item \textbf{Boundary errors only} (37 docs): All items are
    present with no false positives, but at least one item has
    $F_1 < 0.9$. The most affected items are signatures (15 docs,
    where ground truth extends into exhibit content beyond the
    10-K document boundary), item~16 (9 docs, inconsistent ground
    truth conventions), and item~9B (5 docs, trailing Part~III
    header absorption).

  \item \textbf{Missing items only} (21 docs): Dominated by
    signatures (13 docs), where the filing lacks a TOC entry for
    signatures and the fallback detector is suppressed to avoid
    false positives.

  \item \textbf{False positives only} (10 docs): Extra predicted
    items not in ground truth, primarily item~16 (4 docs) in
    filings where the ground truth omits this optional section.

  \item \textbf{Mixed failures} (46 docs): Combinations of the
    above, often involving filings with non-standard HTML structure.
\end{itemize}

\noindent The dominant irreducible error source is the \emph{exhibit
content boundary}: ground truth for signatures and item~16 sometimes
extends into exhibit documents (\texttt{EX-31}, \texttt{EX-32}, etc.)
that reside in separate \texttt{<DOCUMENT>} blocks within the SEC
submission. Since the extraction pipeline operates on the primary
10-K document only, this content is structurally inaccessible.
Approximately 30 of the 114 failures are attributable to this
limitation.


% ===============================================================
\section{Future Directions: Agentic Applications}\label{sec:future}
% ===============================================================

The extraction pipeline produces structured, per-item representations
of 10-K filings at 97.5\% fidelity with 70.9\% document-level
retrieval. This structured output serves as a foundation for
autonomous agent systems that perform financial analysis tasks
requiring targeted access to specific filing
sections~\cite{zhang2023form10k}. We outline several agentic
architectures that build upon the pipeline.

\subsection{Multi-Agent Risk Assessment System}

A system of cooperating agents could perform automated risk
analysis by orchestrating specialized sub-agents:

\begin{description}
  \item[Risk Extraction Agent.]
    Consumes the Item~1A (Risk Factors) slice and applies named
    entity recognition, topic modeling, and sentiment analysis to
    produce a structured risk taxonomy per filing.

  \item[Temporal Comparison Agent.]
    Given risk taxonomies from consecutive fiscal years, identifies
    newly emerged risks, resolved risks, and risks with changed
    severity language. Outputs a year-over-year risk delta report.

  \item[Cross-Company Aggregation Agent.]
    Ingests risk taxonomies across an industry sector (e.g., all
    S\&P~500 technology companies) and identifies systemic risks
    that appear across multiple filings, ranking by prevalence and
    severity.

  \item[Orchestrator Agent.]
    Coordinates the above sub-agents, manages the extraction pipeline
    invocations, and synthesizes a final risk briefing document for
    a human analyst.
\end{description}

\subsection{Autonomous Due Diligence Agent}

An agent tasked with pre-acquisition due diligence could consume
multiple item sections in a structured workflow:

\begin{enumerate}
  \item Extract Item~1 (Business), Item~3 (Legal Proceedings),
    Item~7 (MD\&A), and Item~8 (Financial Statements) for the
    target company's last five fiscal years.
  \item Identify material litigation trends from Item~3 across years.
  \item Extract revenue segments, margins, and management outlook
    from Item~7 and correlate with Item~8 quantitative data.
  \item Produce a structured due diligence memo with flagged
    anomalies, each linked to the source filing and item section.
\end{enumerate}

The pipeline's per-item extraction eliminates the need for the agent
to process entire filings (often 10M+ characters), reducing context
window consumption by 95\% while preserving section-level provenance.

\subsection{Regulatory Compliance Monitoring Agent}

A continuously running agent could monitor SEC EDGAR for new filings
and perform automated compliance checks:

\begin{description}
  \item[Filing Ingestion.]
    Polls EDGAR for new 10-K submissions, runs the extraction
    pipeline, and stores per-item content in a vector database
    with metadata (company, fiscal year, item, CIK).

  \item[Policy Enforcement.]
    Compares extracted Item~9A (Controls and Procedures) and
    Item~9C (Foreign Jurisdiction Disclosures) against a
    configurable rule set encoding regulatory requirements.
    Flags filings that omit required disclosures or contain
    boilerplate language below a specificity threshold.

  \item[Alert Generation.]
    Routes flagged filings to compliance officers with direct
    links to the relevant extracted section, reducing manual
    review time from hours (full filing) to minutes (targeted
    section).
\end{description}

\subsection{Conversational Financial Analyst Agent}

An LLM-based conversational agent could use the extraction pipeline
as a tool within a retrieval-augmented generation (RAG) architecture:

\begin{enumerate}
  \item The user asks: ``What are Apple's main risk factors in
    their 2024 10-K, and how do they compare to 2023?''
  \item The agent invokes the pipeline to extract Item~1A from
    both filings.
  \item The extracted sections (typically 10--50 pages each) are
    chunked, embedded, and indexed in a session-scoped vector store.
  \item The agent retrieves relevant chunks and synthesizes a
    comparative analysis, citing specific passages with page-level
    provenance.
\end{enumerate}

By extracting the relevant section before retrieval, the agent avoids
the noise and irrelevance that arises from embedding and searching
entire filings. This \emph{extract-then-retrieve} pattern improves
both precision and citation accuracy compared to naive full-document
RAG.

\subsection{Portfolio Surveillance Agent Swarm}

A swarm of lightweight agents could monitor a portfolio of holdings:

\begin{description}
  \item[Watcher Agents] (one per holding):
    Each agent tracks its assigned company's EDGAR filings. When a
    new 10-K is published, it extracts all items and computes a
    diff against the prior year's extracted sections.

  \item[Anomaly Detection Agent:]
    Receives diffs from all Watcher Agents. Applies statistical
    and semantic anomaly detection to identify unusual changes:
    significant new risk factors, large swings in reported segment
    revenue, changes in auditor, new legal proceedings, or removal
    of previously disclosed items.

  \item[Portfolio Manager Agent:]
    Aggregates anomaly reports, cross-references with market data
    and news, and produces a daily portfolio surveillance briefing
    ranked by materiality.
\end{description}

This architecture scales linearly with portfolio size and requires
no human intervention for routine monitoring, reserving analyst
attention for flagged anomalies.


% ===============================================================
\section{Conclusion}\label{sec:conclusion}
% ===============================================================

We presented a deterministic, rule-based pipeline for extracting
standardized item sections from SEC 10-K filings. The method exploits
the anchor-link structure of HTML Tables of Contents, classifies
anchors via a three-tier regex hierarchy, and resolves ordering
constraints via dynamic programming. On 392 evaluated filings, the
pipeline achieves a mean character-level $F_1$ of 97.5\% and a
document-level retrieval rate of 70.9\%, with all three evaluation
sets exceeding 96\% mean $F_1$.

The high-fidelity, per-item structured output produced by this
pipeline serves as an enabling primitive for agentic financial
analysis systems. Multi-agent architectures for risk assessment,
due diligence, compliance monitoring, conversational analysis, and
portfolio surveillance can leverage targeted section extraction to
reduce context window consumption, improve retrieval precision, and
maintain provenance to source filings.

% ---------------------------------------------------------------
\printbibliography

\end{document}
